\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Edit separation methods

			\subsubsection{Demucs}
			The Demucs~\cite{demucs} architecture is a deep learning model for musical source separation. It takes as input the stereo mixture, and outputs 4 stereo waveforms corresponding to the stems (vocals, bass, drums and others). Demucs is based on a convolutional encoder, a bidirectional LSTM and a convolutional decoder. The encoder and the decoder are linked with skip U-Net connections. Both the encoder and the decoder are made of 6  blocks, each made of a combination of a convolutional layer with kernel size 8 followed by ReLU activation and a convolution with kernel size 1 followed by gated linear units (GLU). The U-network structure allows the decoder to directly access the input signal and to transfer its phase, improving results.

@@

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcn} (TDCN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data type used for training.

@@

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations. TDCN++, OpenUnmix, and NMF also performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

>>>>

			\subsubsection{Demucs}
			The Demucs~\cite{demucs} architecture is a deep learning model for musical source separation. It takes as input the stereo mixture, and outputs 4 stereo waveforms corresponding to the stems (vocals, bass, drums and other). Demucs is based on a convolutional encoder, a bidirectional LSTM, and a convolutional decoder. The encoder and the decoder are linked with skip U-Net connections. Both the encoder and the decoder are made of 6 blocks, each made of a combination of a convolutional layer with kernel size 8, followed by ReLU activation. Finally there is another convolution with kernel size 1, followed by gated linear units (GLU). The U-network structure allows the decoder to directly access the input signal and to transfer its phase, improving results.

@@

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcn} (TDCN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modeling sequential data, as series of dilated convolutions are a good way to capture temporal patterns.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data used for training.

@@

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations. TDCN++, OpenUnmix, and NMF performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.
